HPC Final Project: A Parallel Implementation of DPG

### 2011-12-08 docs/HPC_report/finalReportJesse.tex
adding notes on scaling to final report
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@91 36274a68-8941-4c93-80ef-affaed5139da
added more lines to hybridized DG formulation
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@92 36274a68-8941-4c93-80ef-affaed5139da

However, this hybridization produces more loosely coupled blocks in the global stiffness matrix than standard DG methods, which, for certain numerical fluxes, will produce the same coupled sparsity pattern as a CG method. For a hybridized DG formulation, the finite element solution is separated into interior degrees of freedom and boundary/flux degrees of freedom. The interior degrees of freedom (which are usually much more than the boundary degrees of freedom) for each element are completely decoupled from each other, meaning that for global assembly of the stiffness matrices, the amount of data communication needed between different processors is reduced.

@@

>>>>

However, this hybridization produces more loosely coupled blocks in the global stiffness matrix than standard DG methods, which, for certain numerical fluxes, will produce the same coupled sparsity pattern as a CG method. For a hybridized DG formulation, the finite element solution is separated into interior degrees of freedom and boundary/flux degrees of freedom. The interior degrees of freedom (which are usually much more than the boundary degrees of freedom) for each element are completely decoupled from each other, implying that, for global assembly of the stiffness matrices, the amount of data communication needed between different processors is reduced. Thus, we expect the parallelizability of the assembly process to be fairly high.

@@

Handicaps
- Batch cache size 
- Using all 12 cores on a single node
